\begin{thebibliography}{99}
\bibitem{jenkins} Jenkins H. Convergence Culture: Where Old and New Media Collide[M]. New York: New York University Press, 2006: 1-24.
\bibitem{goffman} Goffman E. The Presentation of Self in Everyday Life[M]. New York: Doubleday, 1959: 15-76.
\bibitem{marwick} Marwick A E, boyd d. I tweet honestly, I tweet passionately: Twitter users, context collapse, and the imagined audience[J]. New Media \& Society, 2011, 13(1): 114-133.
\bibitem{boyd} boyd d. Social network sites as networked publics[M]//Papacharissi Z. A Networked Self. New York: Routledge, 2010: 39-58.
\bibitem{papacharissi} Papacharissi Z. A Networked Self: Identity, Community, and Culture on Social Network Sites[M]. New York: Routledge, 2010: 304-318.
\bibitem{iwabuchi} Iwabuchi K. Recentering Globalization: Popular Culture and Japanese Transnationalism[M]. Durham: Duke University Press, 2002: 23-51.
\bibitem{azuma} Azuma H. Otaku: Japan's Database Animals[M]. Minneapolis: University of Minnesota Press, 2009: 25-54.
\bibitem{dugay} Du Gay P. Production of Culture/Cultures of Production[M]. London: Sage, 1997: 1-33.
\bibitem{hall} Hall S. Representation: Cultural Representations and Signifying Practices[M]. London: Sage, 1997: 15-30.
\bibitem{turner} Turner G. Understanding Celebrity[M]. London: Sage, 2014: 82-104.
\bibitem{senft} Senft T M. Camgirls: Celebrity and Community in the Age of Social Networks[M]. New York: Peter Lang, 2008: 21-45.
\bibitem{hills} Hills M. Fan Cultures[M]. London: Routledge, 2002: 90-112.
\bibitem{Couldry} Couldry N. Media, Society, World: Social Theory and Digital Media Practice[M]. Cambridge: Polity Press, 2012: 33-61.
\bibitem{Sun} 孙玮. 数字时代的媒介化社会与日常生活重组[J]. 新闻大学, 2020(7): 1-12.
\bibitem{Chen} 陈力丹, 王辰瑶. 新媒体环境下公众人物形象传播机制研究[J]. 国际新闻界, 2019, 41(5): 34-49.
\end{thebibliography}
